plantecophys - an R package for analysis and modelling leaf gas exchange data

### 2015-07-06 manuscript.Rmd
combine fig 1 and 2

```{r fig.width=6, fig.height=5, echo=FALSE, message=FALSE, eval=includeFigs, warn=FALSE}
figure1()
```

** Figure 1**. Leaf photosynthesis - CO~2~ response curve as modelled with the FvC model.

```{r fig.width=6, fig.height=5, echo=FALSE, message=FALSE, eval=includeFigs, warn=FALSE}
suppressWarnings(figure2())
```

** Figure 2**. The intersection of the supply and demand curves of photosynthesis. The `Photosyn` function solves for C~i~ if g~s~, V~cmax~, J~max~ and R~d~ (and other parameters to the FvC model) are known.

```{r fig.width=6, fig.height=5, echo=FALSE, message=FALSE, eval=includeFigs, warn=FALSE}
figure3()
```

**Figure 3**. Standard output from the `fitaci` function. A~net~ is the net photosynthetic rate, C~i~ the intercellular CO~2~ concentration. Symbols are measurements, the line the fitted Farquhar model of photosynthesis.

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs, warn=FALSE}
figure4()
```

**Figure 4**. Visualization of the optimal model of stomatal conductance. Provided we have an estimate of the 'cost of water' ($\lambda$, mol C mol H~2~O^-1^), stomata act to maximize photosynthesis minus transpiration. In (a), individual curves at a range of values for the vapour pressure deficit (D) plots $A-\lambda*E$ versus the C~i~, demonstrating that an optimum exists. The ~FARAO~ function finds this optimum numerically and calculates A~n~ and g~s~. The corresponding response of g~s~ to D is shown in panel (b).

>>>>

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs, warn=FALSE}
figure1()
```

** Figure 1**. (a) Leaf photosynthesis - CO~2~ response curve as modelled with the FvC model. (b) The intersection of the supply and demand curves of photosynthesis. The `Photosyn` function solves for C~i~ if g~s~, V~cmax~, J~max~ and R~d~ (and other parameters to the FvC model) are known.

```{r fig.width=6, fig.height=5, echo=FALSE, message=FALSE, eval=includeFigs, warn=FALSE}
figure2()
```

**Figure 2**. Standard output from the `fitaci` function. A~net~ is the net photosynthetic rate, C~i~ the intercellular CO~2~ concentration. Symbols are measurements, the line the fitted Farquhar model of photosynthesis.

```{r fig.width=8, fig.height=4, echo=FALSE, message=FALSE, eval=includeFigs, warn=FALSE}
figure3()
```

**Figure 3**. Visualization of the optimal model of stomatal conductance. Provided we have an estimate of the 'cost of water' ($\lambda$, mol C mol H~2~O^-1^), stomata act to maximize photosynthesis minus transpiration. In (a), individual curves at a range of values for the vapour pressure deficit (D) plots $A-\lambda*E$ versus the C~i~, demonstrating that an optimum exists. The ~FARAO~ function finds this optimum numerically and calculates A~n~ and g~s~. The corresponding response of g~s~ to D is shown in panel (b).
